DOpElib: Differential Equations and Optimization Environment; A Goal Oriented Software Library for Solving PDEs and Optimization Problems with PDEs

### 2012-12-05 Paper_May_2012/LetterToTheEditior.tex
Christians Comments, and resized a picture so its maximal big without changing the layout.

The article outlines the guiding design principles of our software environment
DOpElib \url{dopelib.net} for the numerical solution of PDEs and optimization problems subject 
to PDEs with special emphasis on modular design of all components. 
We hope that you deem this publication worthy of publication in Computing.

>>>>

The article outlines the guiding design principles of our software environment
DOpElib (see \url{dopelib.net}) for the numerical solution of PDEs and optimization problems subject 
to PDEs with special emphasis on modular design of all components. 
We hope that you deem this publication worthy of publication in Computing.
